---
title: "Presentation"
author: "Thomas Peschel"
date: "25 3 2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with some topics

- Create some data
- Show data

## Slide with R Output

```{r createData,fig.width=16,fig.height=9,out.width="1024px",out.height="768px"}
library(plotly)
n <- 100
data <- data.frame(
  id = 1 : n,
  sex = sample( c( "m", "f "), n, T ),
  x = rnorm( n ),
  y = runif( n ),
  z = rlnorm( n )
)
```

## Slide with Base-Plot

```{r plot_data}
plot( data )
```


## Slide with Plotly Plot

```{r plotly_3d_data,warning=FALSE}
plot_ly( data ) %>%
  add_markers( x = ~ x, y = ~ y, z = ~ z, color = ~sex, type = "scatter3d", mode = "markers", colors = c( "red", "dodgerblue3" ) )
```

## Simply an other Slide
```{r another_slide,warning=FALSE}
plot_ly( data ) %>%
  add_markers( x = ~ x, y = ~ y, z = ~ z, color = ~sex, type = "scatter3d", mode = "markers", colors = c( "red", "dodgerblue3" ) )
```



